Precise spiking motifs in neurobiological and neuromorphic data

### 2022-10-10 manuscript.tex
Update on Overleaf.
1.1

% !TeX TS-program = pdfLaTeX
% !TeX encoding = UTF-8 Unicode
% !TeX spellcheck = en-US
% !BIB TS-program = bibtex
% -*- coding: UTF-8; -*-
% vim: set fenc=utf-8
% https://www.overleaf.com/project/633bf90497b5b325a3ff692e
% https://framateam.org/spikeai/channels/review_polychrony
% https://www.zotero.org/groups/4562620/polychronies
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%  LaTeX support: latex@mdpi.com 
%  For support, please attach all files needed for compiling as well as the log file, and specify your operating system, LaTeX version, and LaTeX editor.

%=================================================================
\documentclass[brainsci,review,submit,pdftex,moreauthors]{Definitions/mdpi} 
% For posting an early version of this manuscript as a preprint, you may use "preprints" as the journal and change "submit" to "accept". The document class line would be, e.g., \documentclass[preprints,article,accept,moreauthors,pdftex]{mdpi}. This is especially recommended for submission to arXiv, where line numbers should be removed before posting. For preprints.org, the editorial staff will make this change immediately prior to posting.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction: Importance of precise spike timings in the brain}\label{sec:time}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Spiking neurons: integrators our synchrony detectors?}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
\note{TODO: a paragraph saying that we think of neurons of integrators, but that they may also switch to a mode fro synchrony detection}~\citep{paugam-moisy_computing_2012}

@@

An important characteristic of neuronal information is that it consists mainly in the transfer of action potentials, or spikes, which consist of brief impulses that propagate along the axons of neurons. These have the particularity of being essentially binary in their amplitude (that is to say, they are prototypical, all or nothing). An important consequence of the speed of processing is that it implies that it is carried out using only very few spikes. Indeed, if we consider that a behavioral response in only 120 ms consists of about ten processing stages following the ``forward'' pathways of the visual system, then this imposes that the processing in a single area is performed with a reduced number of spikes. Neurophysiologists typically use firing sequences to characterize the activity of neurons using different statistics on their individual timing~\citep{perkel_neuronal_1967} but also the dependence across neurons~\citep{perkel_neuronal_1967-1}.

@@

%----------------------------%
\begin{figure}
\centering
\includegraphics{figures/event_driven_computations.png}
\caption{A miniature, event-based ATIS sensor. Contrary to a classical frame-based camera for which a full dense image representation is given at discrete, regularly spaced timings, the event-based camera provides with events at the micro-second resolution. These are sparse as they represent luminance increments or decrements (ON and OFF events, respectively).}\label{fig:silicon_retina}
\end{figure}
%----------------------------%
This section has provided evidence that polychronous groups are an important apsect of information representation in biology with important application in data analysis and neuromorphic engineering. The rest of this review paper is organized as follows.

@@

%----------------------------%
\begin{figure}
\centering
\note{insert fig 2 of izhikevich 2006}
\includegraphics{figures/event_driven_computations.png}
\caption{blah.}\label{fig:PG}
\end{figure}
%----------------------------%

@@

% Please provide either the correct journal abbreviation (e.g. according to the “List of Title Word Abbreviations” http://www.issn.org/services/online-services/access-to-the-ltwa/) or the full name of the journal.
% Citations and References in Supplementary files are permitted provided that they also appear in the reference list here.

\bibliography{references}

>>>>

% !TeX TS-program = pdfLaTeX
% !TeX encoding = UTF-8 Unicode
% !TeX spellcheck = en-US
% !BIB TS-program = bibtex
% -*- coding: UTF-8; -*-
% vim: set fenc=utf-8
% https://www.overleaf.com/project/633bf90497b5b325a3ff692e
% https://framateam.org/spikeai/channels/review_polychrony
% https://www.zotero.org/groups/4562620/polychronies
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% In recognition of your well-respected work, we are inviting you to submit one feature contribution (i.e., a long review or research paper) to an MDPI journal free of charge. If you wish to take advantage of this opportunity, please provide your information and the name of the journal you would like to submit to: https://www.surveymonkey.com/r/XQZ5FP9 (If you cannot find the journal through the link, please feel free to reply to us about your choice).

% The submission deadline for this special offer is 31 October 2022. The journal editorial office will contact you soon once you choose the journal. Please contact the revelant journal’s Editorial Office if you require an extension.

%  LaTeX support: latex@mdpi.com 
%  For support, please attach all files needed for compiling as well as the log file, and specify your operating system, LaTeX version, and LaTeX editor.

%=================================================================
\documentclass[brainsci, %arts,
               review,submit,pdftex,moreauthors]{Definitions/mdpi} 
% For posting an early version of this manuscript as a preprint, you may use "preprints" as the journal and change "submit" to "accept". The document class line would be, e.g., \documentclass[preprints,article,accept,moreauthors,pdftex]{mdpi}. This is especially recommended for submission to arXiv, where line numbers should be removed before posting. For preprints.org, the editorial staff will make this change immediately prior to posting.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction: Importance of precise spike timings in the brain}\label{sec:time}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Spiking neurons: integrators our synchrony detectors?}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Is there a neural code?}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
Neural activity is directly influenced by our neighboring environment, and also by internal states, which in turn allow to generate actions for survival, the ultimate determinant in the light of natural selection. A central question in neuroscience is to better understand this relationship. This is sometimes coined as ``decoding the neural code'', though this would imply that there would be a code, that is an explicit representation within the neural activity. Still, we will use that terminology in all generality. In that regard, it is known that some nervous activity is linked to a specific variable, for instance the stretch of a frog's limb (Galvani). An important characteristic of neuronal information is that it consists mainly in the transfer of action potentials, or spikes, which consist of brief electrochemical impulses that propagate along the axons of neurons. These have the particularity of being essentially binary in their amplitude (that is to say, they are prototypical, all or nothing).  The frequency of those spikes has been shown to be proportional to the stretch in the frog's limb (Adrian) , and this variable (measured in spikes per seconds, or Hertz) is believed to be the major contributor to the neural code. However, computational neuroscience models have hinted that the precise timing may play a crucial role~\citep{paugam-moisy_computing_2012}, an hypothesis which we will review in this manuscript.

@@

An important consequence of the speed of processing is that it implies that it is carried out using only very few spikes. Indeed, if we consider that a behavioral response in only 120 ms consists of about ten processing stages following the ``forward'' pathways of the visual system, then this imposes that the processing in a single area is performed with a reduced number of spikes. Neurophysiologists typically use firing sequences to characterize the activity of neurons using different statistics on their individual timing~\citep{perkel_neuronal_1967} but also the dependence across neurons~\citep{perkel_neuronal_1967-1}.

@@

%----------------------------%
\begin{figure}
\centering
%\includegraphics{figures/event_driven_computations.png}
\caption{A miniature, event-based ATIS sensor. Contrary to a classical frame-based camera for which a full dense image representation is given at discrete, regularly spaced timings, the event-based camera provides with events at the micro-second resolution. These are sparse as they represent luminance increments or decrements (ON and OFF events, respectively).}\label{fig:silicon_retina}
\end{figure}
%----------------------------%
This section has provided evidence that polychronous groups are an important apsect of information representation in biology with important application in data analysis and neuromorphic engineering. The rest of this review paper is organized as follows.

@@

%----------------------------%
\begin{figure}
\centering
\note{insert fig 2 of izhikevich 2006}
%includegraphics{figures/event_driven_computations.png}
\caption{blah.}\label{fig:PG}
\end{figure}
%----------------------------%

@@

% Please provide either the correct journal abbreviation (e.g. according to the “List of Title Word Abbreviations” http://www.issn.org/services/online-services/access-to-the-ltwa/) or the full name of the journal.
% Citations and References in Supplementary files are permitted provided that they also appear in the reference list here. 
%\bibliographystyle{Definitions/chicago2}
\bibliography{references}
